\documentclass[12pt, a4paper]{article}

\usepackage{graphicx}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{cleveref}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{tocloft}
\usepackage{amssymb}
\usepackage{float}
\usepackage{color}

\geometry{margin=1in}
\setlength{\headheight}{17.2pt}
\definecolor{orange}{rgb}{1.0, 0.494, 0.153}

% Header and footer setup
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{Synapse - Group 12}
\fancyfoot[C]{\thepage}

% Section title formatting - reduce spacing and add periods
\titleformat{\section}
  {\large\bfseries}
  {\thesection.}
  {0.25em}
  {}

% Subsection title formatting
\titleformat{\subsection}
  {\normalsize\bfseries}
  {\thesubsection.}
  {0.25em}
  {}

% TOC customization - add dots to all entries and center title
\renewcommand{\cftsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsubsecleader}{\cftdotfill{\cftdotsep}}
\renewcommand{\cftsecaftersnum}{.}
\renewcommand{\cftsubsecaftersnum}{.}
\renewcommand{\cftsecnumwidth}{1.5em}
\renewcommand{\cftsubsecnumwidth}{2em}

% Center TOC title
\renewcommand{\contentsname}{\centering\large\bfseries Table of Contents}
\renewcommand{\cfttoctitlefont}{\hfill}
\renewcommand{\cftaftertoctitle}{\hfill}

% 2. DOCUMENT CONTENT
\begin{document}

% Custom title page
\begin{titlepage}
    \centering
    \vspace*{2cm}

    {\Huge\bfseries Synapse \par}
    \vfill
    {\Large\bfseries Project Proposal \par}
    {\large\bfseries AI Summarisation and Analysis of Resource \par}
    \vspace{1.5cm}

    \vfill
    {\Large \textbf{Group 12}} \\
    \vspace{0.25cm}
    \begin{tabular}{r | l}
        Adrian Cristian Stancu & astan24@student.sdu.dk \\
        Dorina Petra Nagy      & donag24@student.sdu.dk \\
        Tomass Zarins          & tozar24@student.sdu.dk \\
        Jakub Cuninka          & jacun24@student.sdu.dk \\
        Marks Karlins          & mkarl24@student.sdu.dk \\
        Balazs Istvan Nemeth   & banem24@student.sdu.dk \\
    \end{tabular}
    \vspace{1cm}

    {\Large \textbf{Supervisor}} \\
    \vspace{0.25cm}
    \begin{tabular}{r | l}
        Niklas Braun & niklas.braun@speedadmin.com \\
    \end{tabular}

    \vfill
    {\large \today}
\end{titlepage}

\tableofcontents
\newpage

% ===== CONTENT BEGINS HERE =====
\section{Project Background and Problem Statement} \label{sec:problem}

SpeedAdmin develops administrative software for music and art schools. The system manages entities such as students, teachers, lessons, and instruments, and automatically generates logs to record system events and changes.

These logs are essential for traceability and support, but they are highly detailed and often difficult to interpret. A single issue may involve many related log entries across different entities, making it challenging to gain a clear overview. As described in the project case, the logs are granular and verbose, and important information can easily be overlooked.

This creates a practical challenge for both support staff and customers. Understanding log data in a specific context currently requires manual analysis and technical knowledge, which can be time-consuming and inefficient. Therefore, there is a need for a solution that can transform raw log data into structured, understandable insights that better support real-world troubleshooting and analysis.


\section{Aim} \label{sec:aim}
To address the aforementioned issues in \cref{sec:problem} our aim for this project is to design and implement a containerised intelligent software system that enables natural language querying and automated analysis of SpeedAdmin's resource logs.

Users should be able to describe what they are trying to understand in plain language. Based on this input, the system will identify relevant log entries, generate concise summaries, explain them clearly, and highlight potential anomalies or points of interest.

The solution will follow a modular architecture, ensuring that AI components adhere to defined input and output interfaces and can be replaced without major changes to the overall system. The project will demonstrate how intelligent software components can be integrated into a real-world enterprise environment, in line with the given objectives of the course.

\section{Objectives}

To realise the vision outlined in \cref{sec:aim}, we have defined the following objectives. These represent the concrete deliverables and capabilities that the system must provide. Core objectives (marked with *) focus on the essential functionality required for a functional, AI-powered log analysis system capable of meeting SpeedAdmin's requirements, while additional objectives extend the system with enhanced usability and data management features that will be prioritised based on development timeline.

\begin{itemize}
    \item AI-powered log summarisation and anomaly detection based on user prompts{\color{red}\textbf{*}}
    \item Model-agnostic AI pipeline (swappable LLMs via Ollama){\color{red}\textbf{*}}
    \item Containerised microservice architecture (Docker){\color{red}\textbf{*}}
    \item REST API backend (Laravel){\color{red}\textbf{*}}
    \item React frontend for log viewing and prompting
    \item Optional: saving/sharing prompt results (MongoDB)
\end{itemize}

\section{Requirements Analysis}

The following requirements define what the system must do and the qualities it must demonstrate. Functional requirements capture what users can do with the system, while non-functional requirements constrain how it must behave.

\subsection{Functional Requirements} % What the user should be able to do with the system
\begin{itemize}
    \item \textit{Log Ingestion:} The system must be able to ingest and process log data from SpeedAdmin's existing logging infrastructure.
    \item \textit{Log Viewing:} Users should be able to browse and view log entries through the frontend interface, with the ability to filter or search through them.
    \item \textit{Natural Language Querying:} Users should be able to submit natural language prompts against the log data, and the system should return relevant summaries, insights, or detected anomalies in response.
    \item \textit{User Authentication:} Users must authenticate before accessing the system to ensure that only authorised personnel can view or query sensitive log data.
    \item \textit{Optional Data Persistence:} If implemented, users should be able to save or share query results, requiring a database solution (e.g., MongoDB) to store this information.
\end{itemize}
\subsection{Non-Functional Requirements} % How the system should perform or behave
\begin{itemize}
    \item \textit{Performance:} The system should respond to user queries within an acceptable time frame (e.g., under 5 seconds) to ensure a smooth user experience.
    \item \textit{Scalability:} The system should handle increasing volumes of log data and concurrent queries without significant performance degradation.
    \item \textit{Usability:} The interface should be straightforward enough for users of varying technical expertise to operate without prior training.
    \item \textit{Reliability:} The system should handle errors gracefully and remain operational in the face of unexpected conditions, including AI service unavailability.
    \item \textit{Maintainability:} The codebase should be structured to facilitate future changes, with components decoupled sufficiently that one can be modified without breaking others.
    \item \textit{Security:} Sensitive log data must be protected in transit and at rest, and access must be restricted to authenticated and authorised users.
    \item \textit{Regulatory Compliance (GDPR):} The system must not transmit any log data to external or cloud-based services for AI processing. All inference must be performed locally to ensure compliance with GDPR, as log data may contain personally identifiable information.
    \item \textit{Model-Agnostic AI Pipeline:} The AI layer should be designed so that the underlying LLM (e.g., Llama 3, Qwen) can be swapped via Ollama without requiring changes to the rest of the system.
    \item \textit{Containerisation:} All components must be containerised using Docker to ensure environment consistency and ease of deployment.
\end{itemize}

\section{Methodology}
This section outlines the development approach, processes, and tools used throughout the project to ensure structured progress, quality assurance, and effective coordination between all stakeholders.

\subsection{Agile Development and the V-Model}
The project adopts an agile development methodology adapted to the V-Model, striking a balance between iterative delivery and structured verification at each stage. Rather than following a strictly sequential process, the team works in weekly sprints, each encompassing requirements refinement, design decisions, and implementation --- mirroring the left-hand descending side of the V-Model --- followed by corresponding testing and validation activities on the ascending right-hand side.

This structure is reinforced by the project's three-tier stakeholder hierarchy, which maps naturally onto the V-Model:
\begin{itemize}
    \item \textit{Requirements and acceptance criteria} are defined in collaboration with SpeedAdmin and continuously validated through weekly supervisor meetings, forming the outermost level of the V --- requirements elicitation on the left, client acceptance verification on the right.
    \item \textit{System-level design and integration milestones} are overseen by the academic coordinator at the formal checkpoint events defined in the project plan, corresponding to system-level design review and integration testing.
    \item \textit{Implementation and unit testing} are carried out internally by the team of six at the base of the V, within each weekly sprint iteration.
\end{itemize}

Each week, the team holds a brief meeting with the project supervisor (Niklas Braun, SpeedAdmin) on a designated day to review progress and gather feedback on the direction of the work. The team's internal sprint meeting follows immediately after on the same day --- the team simply moves rooms --- allowing any feedback to be addressed in the same session. The academic coordinator is met at the formal milestone points outlined in the project plan, which serve as structured evaluation and system-level validation checkpoints.

\subsection{Version Control and Project Management}
All source code is managed using Git and hosted on GitHub. Changes are introduced through branches following naming conventions (e.g., \texttt{feature/}, \texttt{bugfix/}, \texttt{docs/}) and merged via pull requests, which serve as the primary mechanism for peer code review and quality control before integration.

Project tasks and milestones are tracked using GitHub Issues and a GitHub Projects board, providing the team with a shared view of the development backlog, sprint progress, and upcoming deadlines. Tasks are assigned to specific team members to ensure clear ownership and accountability throughout the project lifecycle.

\subsection{Communication}
Discord serves as the team's primary communication platform. The workspace is structured around a small set of focused channels: a main channel for general coordination and day-to-day discussion, a dedicated channel for supervisor-related communications, and a resources-and-links channel for sharing references and materials. Two voice channels are available for meetings and ad-hoc peer coding sessions.

Meeting scheduling is handled organically in the main channel. For the recurring weekly supervisor meeting, Discord's built-in Events feature is used to set a standing event on the designated day, giving all team members a persistent reminder. The team's internal sprint meeting is scheduled immediately after and in the same manner, as the two sessions run back-to-back.

\section{Architecture}
The system will be designed using a microservice architecture, with the following components and their respective technologies:
\begin{itemize}
    \item \textbf{Frontend} (\texttt{/frontend}): Web application that provides the user interface for viewing logs, inputting queries, and displaying AI-generated responses.
    \item \textbf{Backend} (\texttt{/backend}): Backend framework that serves as the REST API, handling user requests, processing queries, and interacting with the AI models and databases.
    \item \textbf{AI Service} (\texttt{/ai}): Separated service responsible for managing interactions with the LLMs, processing log data, and generating responses based on user queries. \\
          \textit{This service should not impact the backend's ability to function if the AI models are unavailable, and should be designed to handle such scenarios gracefully.}
    \item \textbf{Database} (\texttt{/database}): A relational database instance for storing any necessary structured data, and optionally an unstructured database instance for saving query results if that feature is implemented.
    \item \textbf{Containerisation}: All components of the system will be containerised, ensuring that they can be easily deployed and run in any environment.
\end{itemize}

{\color{orange}\textbf{\textit{TODO: Add diagrams illustrating the architecture and interactions between components. (e.g., a high-level system architecture diagram, sequence diagrams for user interactions, deployment diagrams showing how the containers are orchestrated, etc.)}}}
% TODO: Add diagrams illustrating the architecture and interactions between components. (e.g., a high-level system architecture diagram, sequence diagrams for user interactions, deployment diagrams showing how the containers are orchestrated, etc.)

\subsection{Tech Stack Overview}
The following technologies have been selected to fulfil each component of the architecture described above.
\begin{itemize}
    \item \textit{AI Models:} We will leverage large language models (LLMs) such as Llama 3 or Qwen 2.5, for natural language processing tasks, including log summarisation and anomaly detection.
    \item \textit{Ollama:} This tool will be used to manage and swap between different LLMs without requiring significant code changes.
    \item \textit{Laravel:} This PHP framework will be used to develop the REST API backend that handles user queries and interacts with the AI models.
    \item \textit{React:} The frontend will be built using React to create a responsive and user-friendly interface for viewing logs and inputting queries.
    \item \textit{MSSQL:} Microsoft SQL Server will be used for any necessary relational data storage, such as user information or log metadata.
    \item \textit{Docker:} We will use Docker to containerise the application, ensuring consistency across development, testing, and production environments.
    \item \textit{MongoDB (Optional):} If we choose to implement data persistence for saving or sharing query results, we will use MongoDB as our database solution.
\end{itemize}

\section{Risks and Mitigation Strategies}

The following risks have been identified as potential challenges during the development and deployment of the system. Each risk is accompanied by a mitigation strategy aimed at reducing its likelihood or limiting its impact on project outcomes.

\begin{itemize}
    \item \textbf{AI Model Performance:} The performance of the AI models may not meet expectations, leading to inaccurate or irrelevant responses.

          \textbf{Mitigation:} We will make use of prompt engineering techniques to optimise the performance of the AI models, and we will conduct thorough output testing and validation to ensure that the responses generated by the models are accurate and relevant to user queries.

    \item \textbf{Scalability Issues:} As the volume of log data and user queries increases, it may exceed the model's context window or lead to performance degradation.

          \textbf{Mitigation:} We will design the system with scalability in mind, implementing strategies such as log filtering, summarisation and chunking to manage large volumes of data, and optimising the AI pipeline to handle increased load efficiently.

    \item \textbf{LLM performance on available hardware:} The language models may be constrained by the available hardware resources, particularly VRAM and compute capacity, which could lead to slow inference times or an inability to run larger models altogether.

          \textbf{Mitigation:} We will test early and often to ensure that the selected models perform acceptably on our available hardware, and we will fall back to quantized model variants where necessary to reduce resource requirements while maintaining acceptable response quality. Additionally, we will implement a request queuing mechanism so that concurrent AI requests are handled gracefully without overloading the inference pipeline.

    \item \textbf{Team unfamiliarity with technologies:} Some team members may be unfamiliar with certain technologies or frameworks used in the project, which could lead to delays or challenges in development.

          \textbf{Mitigation:} We will allocate time for team members to learn and familiarise themselves with any new technologies, and we will encourage knowledge sharing and collaboration within the team to ensure that everyone is up to speed.
\end{itemize}

\section{Project Organization}
The project will be developed by a team of 6 members. Since a core objective of this project is learning, no fixed roles are assigned. Rather than optimising for delivery efficiency, each team member is expected to actively contribute across all areas of the system --- backend development, frontend development, AI integration, and DevOps --- gaining hands-on experience with every component.

This means that while tasks will naturally be distributed at any given point in time to ensure steady progress, every member is expected to work in each area over the course of the project. Members are encouraged to rotate responsibilities, pair on unfamiliar tasks, and share knowledge so that by the end of the project, the entire team has a thorough understanding of how each component works, how they interact, and the design decisions behind them.

\section{Project Plan}

The following table outlines the planned schedule for the project, organised by week with corresponding dates and development focus areas.

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.5}
    \begin{tabular}{|c|c|c|}
        \hline
        \textbf{Week} & \textbf{Dates}  & \textbf{Focus}                                        \\
        \hline
        8--9          & 19 Feb -- 5 Mar & Architecture design, repo setup, Docker skeleton      \\
        \hline
        10            & 5 Mar           & Proposal submission                                   \\
        \hline
        11--13        & 12--26 Mar      & Core backend API + DB connection, AI service skeleton \\
        \hline
        14            & Easter Break    & \multicolumn{1}{c|}{\textit{No work planned}}         \\
        \hline
        15            & 9 Apr           & Midterm seminar                                       \\
        \hline
        16            & 16 Apr          & Midterm evaluation                                    \\
        \hline
        17--19        & 23 Apr -- 7 May & Frontend, AI pipeline integration, prompt engineering \\
        \hline
        20--21        & 14--21 May      & Testing, validation, report writing                   \\
        \hline
        22            & 28 May          & Final presentation                                    \\
        \hline
        23            & 2 Jun           & Code + report submission                              \\
        \hline
    \end{tabular}
\end{table}


\section{Tentative Report Outline}
\begin{itemize}
    \item \textbf{Introduction:} Overview of the project, its background, and objectives.
    \item \textbf{Problem Analysis:} In-depth analysis of the problem being addressed, including any challenges or constraints encountered during development.
    \item \textbf{Requirements}: Comprehensive list of functional and non-functional requirements, along with any changes or updates made during the project.
    \item \textbf{Methodology:} Detailed description of the methods and technologies used in the project, including system architecture and design decisions.
    \item \textbf{Design}: Explanation of the system architecture, components, and interactions, supported by diagrams and illustrations.
    \item \textbf{Implementation:} Explanation of the development process, challenges faced, and how they were addressed.
    \item \textbf{Validation:} Discussion of how the results were validated, including testing methodologies and any limitations of the validation process.
    \item \textbf{Conclusion:} Summary of the project achievements and final thoughts.
\end{itemize}

\end{document}